Timely Object Recognition

### 2012-06-01 writeups/nips12/introduction.tex
trevor's edits incorporated

The computer vision field has converged on a general method for object detection, and a standard evaluation of results.
Efficiency is not a concern of the evaluation metrics, and the methods are not evaluated in an inherently multi-class setting.
However, in most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.

In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.

In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
Furthermore, the value of the answer depends on the target application.

@@

A hypothetical recognition system for a vision-based advertising deployment presents a case study.
The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
The detection strategy to maximize profit in such an environment should depend on all of these variables.

We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
\emph{What is the best performance we can get on a budget?}
To answer it, we consider the evaluation metric of performance vs. time, shown in Figure~\ref{fig:figure1} and discussed further in the text.

We present a method that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.

>>>>

In most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.
In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.
In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.

@@

The conventional approach to evaluation of results on visual category
recognition does not consider efficiency and evaluates performance
indepednently across classes.  
We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
\emph{What is the best performance we can get on a budget?}
We propose a new \emph{timeliness} measure of performance vs. time (shown in Figure~\ref{fig:figure1}), which evalutes the time efficiency of multi-class detection.

We present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.

A hypothetical recognition system for a vision-based advertising deployment presents a motivational case study.
The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
The detection strategy to maximize profit in such an environment should depend on all of these variables.
We explore this scenario using the PASCAL VOC datasets and evaluation regimes, and show that our learned dynamic policy offers a better strategy than a random or optimal static ordering of detectors.

### 2012-06-01 writeups/nips12/nips2012.tex
trajectories figure in
trevor's edits incorporated

\documentclass{article} % For LaTeX2e
\usepackage{nips12submit_e,times}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{color}
\usepackage{subfig}
\usepackage{natbib}
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{subfigure}

@@

\begin{abstract}
In a large visual multi-class detection framework, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our method for multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
In contrast to previous work, our method significantly diverts from the predominant greedy strategies and therefore learns to employ actions without any immediate reward for the goal of detection.
We evaluate our method with respect to performance in the novel Average Precision (AP) vs. Time evaluation on the widely used PASCAL VOC object detection dataset.
With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation. At time of publication we will make our code available, which is easily extendible to new detectors, classifiers, tasks and reward functions due to the modular nature of our formulation.
\end{abstract}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips12submit_e,times}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{color}
\usepackage{subfig}
\usepackage{natbib}
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

@@

\begin{abstract}
In a large visual multi-class detection framework, the timeliness of results can be crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our method for \emph{timely multi-class detection} aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
In contrast to previous work, our method significantly diverts from the predominant greedy strategies, and is able to learn to employ actions with deferred value.
We evaluate our method with respect to performance on a novel \emph{timeliness} measure, computed as the area under an Average Precision (AP) vs. Time
curve.
We conduct experiments on the widely used PASCAL VOC object detection dataset.
With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation on PASCAL VOC.
% At time of publication we will make our code available, which is easily extendible to new detectors, classifiers, tasks and reward functions due to the modular nature of our formulation.
\end{abstract}
